\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-14 trunk/arch.tex
Some tweaking in the figures

\begin{figure}[!htb]
 \centering
 \includegraphics[scale=0.45]{figs/AUV-agent.pdf}
 \caption{\small A \rx agent is composed of multiple reactors or
   control loops (rounded boxes) which are connected through state
   variables provided by one reactor ({\color{blue}blue} solid line)
   with multiple possible clients ({\color{green}green} dashed lines)}
  \label{fig:agent}
\end{figure}

@@

\item The future objectives a reactor has on \textsf{Internal} state
  will likely imply sub-objectives to be reported to the owner of its
  {\em external} state variables depending on their current
  values. Should the \textsf{Pilot} want to visit a specific
  \textsf{Waypoint} -- given its current position as provided by
  \textsf{Sensor\_Data}, it can identify a sequence of
  \textsf{Nav\_cmd} states that should eventually help it reach this
  location. \comment{this explanation could do with a figure which I
    believe we have used previously}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.45\columnwidth]{figs/TREX_flow}
  \vskip-1cm
  \caption{Illustration of state information flow between the
    \texttt{Pilot} and the \texttt{Vehicle} reactors.
    Observations transit in a bottom-up during synchronization 
    and apply to the execution frontier $\tau$. 
    Goal information flow from the top to the bottom and concern the
    desired future values of state variables.}
  \label{fig:trex:flow}
\end{figure}

Given the above example, the \rx architecture therefore helps abstract
reactor interaction by constraining them to state variables. Each
reactor is therefore agnostic where its {\em external} state
information is managed as long as this information is available and
properly maintained for managing {\em internal} state
information. This {\em internal} state in turn may be used by other
reactors. Such a formalism also constrains reactor interaction to
state information exchange which comes in two forms:

@@

\item {\em Observation on current state values}: This information
  propagates \emph{up} in the reactor dependency graph at the
  synchronization phase and occurs at the beginning of every
  tick. During this phase the agent provides updates to each reactor
  on their {\em external} state variables for this tick so as they
  could compute their {\em internal} state variable values for this
  same tick. By doing so we propagate a consistent view of that state
  of the world throughout all the reactors as time
  advances. \comment{could do with a figure here}

\item {\em Goal request on future state}: This information propagates
  \emph{down} in the reactor dependency graph. In order to satisfy own
  {\em internal} objectives, a reactor may have a plan that relies on
  future values of one of its {\em external} state. When such a plan
  is identified the agent ensures that this part of the plan is given
  as a goal to the owner of the given {\em external} state
  variable(s). \comment{could do with a figure here}

>>>>

\begin{figure}[!htb]
  \centering
  \subfloat[\small A \rx agent is composed of multiple reactors or
    control loops (rounded boxes) which are connected through state
    variables provided by one reactor ({\color{blue}blue} solid line)
    with multiple possible clients ({\color{green}green} dashed
    lines)]{\includegraphics[scale=0.45]{figs/AUV-agent.pdf}
  \label{fig:agent}
  }
  \qquad
  \subfloat[\small State information flow between the
    \texttt{Pilot} and the \texttt{Vehicle} reactors.
    Observations transit as a bottom-up flow 
    and apply to the execution frontier $\tau$. 
    Goal information flow from the top to the bottom and relates to 
    desired future values of state variables.]{
      \includegraphics[width=0.4\columnwidth]{figs/TREX_flow}
      %\vskip-1cm
      \label{fig:trex:flow}
    }
    \caption{\rx connection of reactors through state variables based on the
    AUV agent we use at sea.}
\end{figure}

@@

\item The future objectives a reactor has on \textsf{Internal} state
  will likely imply sub-objectives to be reported to the owner of its
  {\em external} state variables depending on their current
  values. Should the \textsf{Pilot} want to visit a specific
  \textsf{Waypoint} -- given its current position as provided by
  \textsf{Sensor\_Data}, it can identify a sequence of
  \textsf{Nav\_cmd} states that should eventually help it reach this
  location. %\comment{this explanation could do with a figure which I
    %believe we have used previously}

@@

Given the above example, the \rx architecture therefore helps abstract
reactor interaction by constraining them to state variables. Each
reactor is therefore agnostic where its {\em external} state
information is managed as long as this information is available and
properly maintained for managing {\em internal} state
information. This {\em internal} state in turn may be used by other
reactors. Such a formalism also constrains reactor interaction to
state information exchange which comes in two forms as illustrated in
Figure \ref{fig:trex:flow}:

@@

\item {\em Observation on current state values}: This information
  propagates \emph{up} in the reactor dependency graph at the
  synchronization phase and occurs at the beginning of every
  tick. During this phase the agent provides updates to each reactor
  on their {\em external} state variables for this tick so as they
  could compute their {\em internal} state variable values for this
  same tick. By doing so we propagate a consistent view of that state
  of the world throughout all the reactors as time
  advances. %\comment{could do with a figure here}

\item {\em Goal request on future state}: This information propagates
  \emph{down} in the reactor dependency graph. In order to satisfy own
  {\em internal} objectives, a reactor may have a plan that relies on
  future values of one of its {\em external} state. When such a plan
  is identified the agent ensures that this part of the plan is given
  as a goal to the owner of the given {\em external} state
  variable(s). %\comment{could do with a figure here}
